Legends for supplementary material

### 2019-04-05 Manuscript/Supplementary/supplementary_legends.Rmd
added figures to supplementary and updated legends

**Supplementary Figure 1. Distance Densities across cell lines and resolutions.** Density curves of distances (in millions of base pairs) from genomic bins to flanked TAD boundaries for 10 kb (A), 25 kb (B), 50 kb (C), and 100 kb (D) data resolutions across the GM12878 (left column) and K562 (right column) cell lines. The untransformed distance densities are filled in red, while the $log_{2}$ tranformed distance densities are filled in blue.

>>>>

**Supplementary Figure 1. Distance Densities Across Cell Lines and Resolutions.** Density curves of distances (in millions of base pairs) from genomic bins to flanked TAD boundaries for 10 kb (A), 25 kb (B), 50 kb (C), and 100 kb (D) data resolutions across the GM12878 (left column) and K562 (right column) cell lines. The untransformed distance densities are filled in red, while the $log_{2}$ tranformed distance densities are filled in blue.

**Supplementary Figure 2. Clustered Correlogram for Genomic Annotations at the 10 kb Resolution for the GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome. Positive correlations are denoted in red, while negative correlations are denoted in blue. The upper triangular matrix of correlations was clustered using Ward's method. Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.

**Supplementary Figure 3. Clustered Correlogram for Genomic Annotations at the 10 kb Resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome. Positive correlations are denoted in red, while negative correlations are denoted in blue. The upper triangular matrix of correlations was clustered using Ward's method. Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.

**Supplementary Figure 4. Clustered Correlogram for Genomic Annotations at the 25 kb Resolution for GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome. Positive correlations are denoted in red, while negative correlations are denoted in blue. The upper triangular matrix of correlations was clustered using Ward's method. Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.

**Supplementary Figure 5. Clustered Correlogram for Genomic Annotations at the 25 kb Resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome. Positive correlations are denoted in red, while negative correlations are denoted in blue. The upper triangular matrix of correlations was clustered using Ward's method. Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.

**Supplementary Figure 6. Clustered Correlogram for Genomic Annotations at the 50 kb Resolution for GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome. Positive correlations are denoted in red, while negative correlations are denoted in blue. The upper triangular matrix of correlations was clustered using Ward's method. Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.

**Supplementary Figure 7. Clustered Correlogram for Genomic Annotations at the 50 kb Resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome. Positive correlations are denoted in red, while negative correlations are denoted in blue. The upper triangular matrix of correlations was clustered using Ward's method. Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.

**Supplementary Figure 8. Clustered Correlogram for Genomic Annotations at the 100 kb Resolution for GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome. Positive correlations are denoted in red, while negative correlations are denoted in blue. The upper triangular matrix of correlations was clustered using Ward's method. Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.

**Supplementary Figure 9. Clustered Correlogram for Genomic Annotations at the 100 kb Resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome. Positive correlations are denoted in red, while negative correlations are denoted in blue. The upper triangular matrix of correlations was clustered using Ward's method. Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
